An equivalence of compositional frameworks

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
getting ready for equivalence chapter

\begin{itemize}
\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
\end{itemize}

@@

\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction. Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}. 
The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of (pseudo) double categories are recalled in \cref{sec:doublecats}.

@@

\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
\begin{comment}

@@

>>>>

\begin{itemize}
\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix. Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration. The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category. Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
\end{itemize}

@@

\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction. Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}. 
The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.

@@

\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
%\begin{comment}

@@

%\end{comment}
